---
output: html_document
editor_options: 
  chunk_output_type: console
---
White Wine Exploration by Mohammad Albloushi
========================================================


```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# loading the required libraries
library(ggplot2)
library(GGally)
library(gridExtra)
library(RColorBrewer)

```

```{r echo=FALSE, Load_the_Data}
# Load the Data
winedata <- read.csv('wineQualityWhites.csv')
```

### Introduction
In this project i'm going to explore this data set using data analysis techniques, with an objective of finding Which chemical properties influence the quality of white wines.

This tidy data set contains 4,898 white wines with 13 variables on quantifying the chemical properties of each wine. At least 3 wine experts rated the quality of each wine, providing a rating between 0 (very bad) and 10 (very excellent).

Read this [text file](https://s3.amazonaws.com/udacity-hosted-downloads/ud651/wineQualityInfo.txt) which describes the variables and how the data was collected.

### Summary of the data:

```{r echo=FALSE}
dim(winedata)
```
There are **4898** observations and **13** variables.

```{r echo=FALSE}
names(winedata)
```
These are the variable names.

```{r echo=FALSE}
str(winedata)
```
All of the variables are numerical variables except for **X** And **Quality** which are integer,The **X** Variable is just an index variable for each observation.

```{r echo=FALSE}
summary(winedata)
```
We can quickly observe a few things from the above summary:

- White wine **Quality** range is from **3** to **9** with a median of **6** (There is no perfect wine with a quality of 10).

- **Residual Sugar**, **Free Sulfur Dioxide** And **total.sulfur.dioxide** has a maximum value way higher than the median (Which mean there is outliers).

- **Density** Have very close numbers ranging from almost **0.98** to **1.05**.

### Creating a new variable
I'm going to add a factor variable called **Rating** which will help us tell which wine got **High**, **Average** or **Low** ratings, All of our variables are either numerical or integer, This is going to be helpful for investigating further in our analysis. 
I'm going to make a bucket for quality scores as:

- 0 to 4 : **Bad**
- 5 to 6 : **Average**
- 7 to 10 : **Good**

```{r}
winedata$rating <- cut(winedata$quality, # Creating a bucket from the quality variable.
                       c(0, 4, 6, 10), 
                       labels = c('Bad', 'Average', 'Good'))
```
```{r echo=FALSE}
summary(winedata$rating)
```
Most of the wine has an **Average** rating, and there's more **Good** wine than **Bad** wine.

# Univariate Plots Section

### Quality

```{r echo=FALSE}
ggplot(aes(x = quality), data = winedata) +
  geom_histogram(binwidth = 0.5) +
  scale_x_continuous(breaks = seq(3,10,1))
summary(winedata$quality)
```
 
Most of the values lie between **3** and **9** with a peek at **6**, The distribution seems to be normal.
 
### Fixed Acidity

```{r echo=FALSE}
ggplot(aes(fixed.acidity), data = winedata) +
  geom_histogram(binwidth = 0.5, color = 'black') +
  scale_x_continuous(breaks = seq(3,15,1))
summary(winedata$fixed.acidity)
```

The values in **Fixed Acidity** lie between **3.8** and **14.20**, This histogram show's that there is only a few values less than **4** and more than **10** so i'm going to limit my values in the next histogram.

```{r echo=FALSE, warning=FALSE}
ggplot(aes(x = fixed.acidity), data = winedata) +
  geom_histogram(binwidth = 0.2, color = 'black') +
  scale_x_continuous(breaks = seq(4,10,1), limits = c(4, 10))
```

The distribution is normal now and most of the fixed acidity is between **6** to **8**.

### Volatile Acidity

```{r echo=FALSE}
ggplot(aes(x = volatile.acidity), data = winedata) +
  geom_histogram(binwidth = 0.02, color = 'black') +
  scale_x_continuous(breaks = seq(0.1, 1.5, 0.05))
summary(winedata$volatile.acidity)
```

The values in this histogram lie between **0.0800** and **1.1**, From this histogram i can see that there are few values as well under **0.1** and more than **0.65** so i'm going to adjust it.

```{r echo=FALSE, warning=FALSE}
ggplot(aes(x = volatile.acidity), data = winedata) +
  geom_histogram(binwidth = 0.02, color = 'black') +
  scale_x_continuous(breaks = seq(0,1.5,0.05), limits = c(0.1, 0.65))
```

This distribution is slightly positively skewed as we can see, Most of the volatile acidity is between **0.2** and **0.3**.

### Citric Acid

```{r echo=FALSE}
ggplot(aes(x = citric.acid), data = winedata) +
  geom_histogram(binwidth = 0.03, color = 'black') +
  scale_x_continuous(breaks = seq(0, 2, 0.1))
summary(winedata$citric.acid)
```

The values lie between **0** and **1.6600** which and from the histogram we can see that there seems to be values around 0, We can see values after **0.75** with less count, Which makes our histogram long tailed so i will limit it in the next histogram.

```{r echo=FALSE, warning=FALSE}
ggplot(aes(x = citric.acid), data = winedata) +
  geom_histogram(binwidth = 0.01, color = 'black')+
  scale_x_continuous(breaks = seq(0, 2, 0.05), limits = c(0, 0.75))
```

Now the distribution looks normal and we can see the distribution in a better way, Most of the values lies between **0.20** and **0.50** and there is a big bar around **0.48**.

### Residual Sugar

```{r echo=FALSE}
ggplot(aes(x = residual.sugar), data = winedata) +
  geom_histogram(binwidth = 1, color = 'black')
summary(winedata$residual.sugar)
```

75% of our values are less than **9.900** and the max is **65.800**, I can't really understand a lot in this histogram so i'm going to use **log 10** to understand the long tail distribution.

```{r echo=FALSE, warning=FALSE}
ggplot(aes(x = residual.sugar), data = winedata) +
  geom_histogram(binwidth = 0.03, color = 'black') +
  scale_x_log10(breaks = c(1,1.5,2,3,4,5,7,10,15,20,30))
```

Using **log10** i can see a bimodal distribution, there's multiple peaks in the histogram, One of them is between **1** and **2.5**, There a small peeks between **1** and **1.5** with low count surrounded by high peeks.

### Chlorides

```{r echo=FALSE}
ggplot(aes(x = chlorides), data = winedata) +
  geom_histogram(binwidth = 0.005, color = 'black')
summary(winedata$chlorides)
```

The range for **Chlorides** is between **0.00900** and **0.34600**, Just like **Residual Sugar** i'm going to use **log 10** the better understand the histogram.

```{r echo=FALSE, warning=FALSE}
ggplot(aes(x = chlorides), data = winedata) +
  geom_histogram(binwidth = 0.03, color = 'black') +
  scale_x_log10(breaks = c(0.01, 0.02, 0.03, 0.04, 0.05, 0.07, 0.10, 0.15, 0.20, 0.30))
```

When I used **log 10** I can see that most values lies between **0.03** and **0.06**, And the distribution look's normal.

### Free Sulfur Dioxide

```{r echo=FALSE}
ggplot(aes(x = free.sulfur.dioxide), data = winedata) +
  geom_histogram(binwidth = 4, color = 'black') +
  scale_x_continuous(breaks = seq(0, 290, 10))
summary(winedata$free.sulfur.dioxide)
```

From looking at this histogram I can detect outliers , the median for **Free Sulfur Dioxide** is **34** and The maximum is **289**, I'm going to limit my values in the next histogram.

```{r echo=FALSE, warning=FALSE}
ggplot(aes(x = free.sulfur.dioxide), data = winedata) +
  geom_histogram(binwidth = 2, color = 'black') +
  scale_x_continuous(breaks = seq(0, 80, 5), limits = c(0, 80))
```

The distribution looks almost like a perfect normal distribution now, The highest peak happened around **27** and **28**.

### Total Sulfure Dioxide

```{r echo=FALSE}
ggplot(aes(x = total.sulfur.dioxide), data = winedata) +
  geom_histogram(binwidth = 5, color = 'black') +
  scale_x_continuous(breaks = seq(10,440,20))
summary(winedata$total.sulfur.dioxide)
```

I can detect a few outliers in these values since 75% of our data is under **167** and our maximum is **440**, I'm going to limit our values to better understand the histogram.

```{r echo=FALSE, warning=FALSE}
ggplot(aes(x = total.sulfur.dioxide), data = winedata) +
  geom_histogram(binwidth = 5, color = 'black') +
  scale_x_continuous(breaks = seq(10, 260, 10), limits = c(10,260))
```

The distribution look's normal with the highest peak from **95** to **160**.

### Density

```{r echo=FALSE}
ggplot(aes(x = density), data = winedata) +
  geom_histogram(binwidth = 0.0010, color = 'black') + 
  scale_x_continuous(breaks = seq(0.98,1.05,0.01))
summary(winedata$density)
```

This distribution is hard to work with because it has such low and close numbers, i can tell by just looking at the histogram that most data lie somewhere between **0.98** and **1** so i'm going to limit my values to understand and see the values.

```{r echo=FALSE, warning=FALSE}
ggplot(aes(x = density), data = winedata) +
  geom_histogram(binwidth = 0.00050, color = 'black') + 
  scale_x_continuous(breaks = seq(0.98,1.005,0.0010), limits = c(0.9871,1.003))
```

This is much better the distribution look's normal and I can't see the values clearly now, I can observe that the most peeks happened between **0.991** and **0.996**.

### pH

```{r echo=FALSE}
ggplot(aes(x = pH), data = winedata) +
  geom_histogram(binwidth = 0.02, color = 'black') + 
  scale_x_continuous(breaks = seq(2.7, 3.9, 0.1))
summary(winedata$pH)
```

This distribution look normal with most values lies between **3.1** and **3.3**.

### Sulphates

```{r echo=FALSE}
ggplot(aes(x = sulphates), data = winedata) +
  geom_histogram(binwidth = 0.02, color = 'black') +
  scale_x_continuous(breaks = seq(0, 1.5, 0.1))
summary(winedata$sulphates)
```

**Sulphates** histogram look's slightly positively skewed with the highest peak around **0.4** and **0.5**.

### Alcohol

```{r echo=FALSE}
ggplot(aes(x = alcohol), data = winedata) +
  geom_histogram(binwidth = 0.2, color = 'black') +
  scale_x_continuous(breaks = seq(8, 15, 0.5))
summary(winedata$alcohol)
```

The distribution is positively skewed and the highest peak happened around **9.4**.

# Univariate Analysis

### What is the structure of your dataset?
In this data set there are **12** variables (Without the X Variable) and **4898** observations, I Also created a new variable called **Rating** which classify the quality of the wine (13 Variables), All of our data is numerical except for **Quality** and **Rating**.

### What is/are the main feature(s) of interest in your dataset?
My main feature is **Quality**, I'm trying to detect which chemical properties influence the **Quality** of white wines.

### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?
It's hard to guess which feature influence the quality of wine because most of the plots have normal distribution, but if i have to guess it's going to be **Residual Sugar** and **Alcohol**.

### Did you create any new variables from existing variables in the dataset?
Yes i created a new variable called **Rating** which basiclly classify the **Quality** of wines to **Bad**, **Average** and **Good**.

### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?
I did multiple operation to adjust my histograms, one of them is **Residual Sugar** it had a positive skew but after i performed log 10 on the scale it gave me a bimodel distribution.

# Bivariate Plots Section

I'm going to use a correlation matrix to get the strongest correlations for **Quality** and other strong correlations.

```{r echo = FALSE}
ggcorr(data = winedata[2:13], label = TRUE, label_alpha = TRUE, label_round = 3,
  size = 3, hjust = 0.75, nbreaks = 6, angle = -75, label_size = 3)
```

This correlation matrix shows us that the strongest correlation for quality is:

- **Quality x Alcohol (0.436)**
- **Quality x Density (-0.307)**
- **Quality x Chlorides (-0.21)**

We can also observe that the top 5 strongest correlations are :

- **Density x Residual Sugar (0.839)**
- **Density x Alcohol (-0.78)**
- **Total Sulfur Dioxide x Free Sulfur Dioxide (0.616)**
- **Density x Total Sulfur Dioxide (0.53)**
- **Alcohol x Residual Sugar (-0.451)**

Since I'm interested in which properties affect the **Quality** of wine i'm going to quickly box plot each chemical properties into a box plot and limit 1% from it to observe any patterns in the box plot that might be interesting to look at.

```{r echo=FALSE}

# Creating a function to make things easier and faster
boxplot_quality <- function(variable){
  ggplot(data = winedata, aes(x = ordered(quality), y = (variable))) +
    geom_boxplot(alpha = 5/10) +
    coord_cartesian(ylim = quantile((variable), c(0.01, 0.99)))
}

# Saving each plot into a variable
p1 <- boxplot_quality(winedata$alcohol) +
  ylab(label = "Alcohol")

p2 <- boxplot_quality(winedata$residual.sugar) +
  ylab(label = "Residual Sugar")

p3 <- boxplot_quality(winedata$density) +
  ylab(label = "Density")

p4 <- boxplot_quality(winedata$fixed.acidity) +
  ylab(label = "Fixed Acidty")

p5 <- boxplot_quality(winedata$volatile.acidity) +
  ylab(label = "Volatile Acidty")

p6 <- boxplot_quality(winedata$citric.acid) +
  ylab(label = "Citric Acid")

p7 <- boxplot_quality(winedata$chlorides)+
  ylab(label = "Chlorides")

p8 <- boxplot_quality(winedata$free.sulfur.dioxide) +
  ylab(label = "Free Sulfur Dioxide")

p9 <- boxplot_quality(winedata$total.sulfur.dioxide) +
  ylab(label = "Total Sulfur Dioxide")

p10 <- boxplot_quality(winedata$pH) +
  ylab(label = "pH")

p11 <- boxplot_quality(winedata$sulphates) +
  ylab(label = "Sulphates")

# Plotting the variables together
grid.arrange(p1,p2,p3,p4,p5,p6,p7,p8,p9,p10,p11, ncol = 4)
```

The relationships worth looking into is :

- **Quality x Alcohol**
- **Quality x Density**
- **Quality x Chlorides**
- **Quality x pH**
- **Quality x Total Sulfur Dioxide**
- **Quality x Volatile Acidity **

Let's look closely into these Relationships.

### Quality x Alcohol

```{r echo=FALSE}
# First i will make a function that makes boxplot + jitter + smooth line
boxplot_jitter <- function(variable){
  ggplot(data = winedata, aes(x = quality, y = (variable))) +
    geom_boxplot(aes(group=quality,color = 'red')) +
    geom_jitter(alpha = 0.25/10, color = 'blue') +
    stat_smooth(method = 'lm', color = 'light green') +
    scale_x_continuous(breaks = seq(0,10,1))
}
```

```{r echo=FALSE}
boxplot_jitter(winedata$alcohol) +
  ylab(label = "Alcohol")
by(winedata$alcohol, ordered(winedata$quality), summary)
```

We know that **Alcohol** has the strongest correlation with **Quality**, And it's showing in the plot that alcohol has in fact effect on the quality of the wine,The median for **Quality** of 4 is **10.10** and the median for **Quality** of 8 is **12**, We can see after quality 5 as the **Alcohol** increases the **Quality** of the wine increases.

### Quality x Density

```{r echo=FALSE}
boxplot_jitter(winedata$density) +
  coord_cartesian(ylim = c(0.985,1.005)) +
  ylab(label = "Density")
by(winedata$density, ordered(winedata$quality), summary)
```

**Quality** and **Density** have a negative relationship as shown in the plot, if we don't include **Quality** 3 and 4 we can see that as the density decrease the rating increase.

### Quality x Chlorides

```{r echo=FALSE}
boxplot_jitter(winedata$chlorides) +
  coord_cartesian(ylim = c(0,0.1)) +
  ylab(label = "Chlorides")
by(winedata$chlorides, ordered(winedata$quality), summary)
```

We can see that we have a negative relationship between **Quality** and **Chlorides**, if we don't include **Quality** of 3 we can observe as the **Chlorides** decrease the quality increase.

### Quality x pH

```{r echo=FALSE, warning=FALSE}
boxplot_jitter(winedata$pH) +
  ylab(label = "pH")
by(winedata$pH, ordered(winedata$quality), summary)
```

Here we have a positive correlation, we can see the median for **Quality** increases as the **pH** increase.

### Quality x Total Sulfur Dioxide

```{r echo=FALSE, warning=FALSE}
boxplot_jitter(winedata$total.sulfur.dioxide)+
  coord_cartesian(ylim = c(10,260)) +
  ylab(label = "Total Sulfur Dioxide")
by(winedata$total.sulfur.dioxide, ordered(winedata$quality), summary)
```

Here we can see an odd boxplot, we can see a **Quality** of 4 is much lower than every other **Quality**, but if we don't include it in our boxplot it will show us as the **Total Sulfur Dioxide** decreases the **Quality** increases.

### Quality x Volatile Acidity

```{r echo=FALSE, warning=FALSE}
boxplot_jitter(winedata$volatile.acidity) +
  coord_cartesian(ylim = c(0.1, 0.65)) +
  ylab(label = "Volatile Acidity")
by(winedata$volatile.acidity, ordered(winedata$quality), summary)
```

Here we have an odd box plot as well, We can observe that after **Quality** of 4 we can see that when the **Volatile Acidity** increase, We get a higher **Quality**, But it stops at a **Quality** of 7, we can see then the **Quality** of 8 and 9 have a little bit higher **Volatile Acidity** than **Quality** of 5 to 7.

Now let's look at the strongest correlations other than **Quality**.

### Residual Sugar x Density

```{r echo=FALSE, warning=FALSE}
ggplot(aes(x = residual.sugar, y = density), data = winedata) +
  geom_jitter(alpha = 5/10) +
  coord_cartesian(ylim = c(0.985, 1.005), xlim = c(0, 30)) +
  geom_smooth(method = 'gam', formula = y ~ s(x, bs = "cs"))
```

Using scale log 10 on **Residual Sugar** gives a strong positive relationship between ** Residual Sugar** and **Density**, we can observe that having high sugar will lead to having higher **Density**.

### Alcohol x Density

```{r echo=FALSE, warning=FALSE}
ggplot(aes(x = alcohol, y = density), data = winedata) +
  geom_jitter(alpha = 5/10) +
  coord_cartesian(ylim = c(0.985, 1.005)) +
  geom_smooth(method = 'gam', formula = y ~ s(x, bs = "cs"))
```

Here we have also a strong relationship, But it's negative, it's almost the opposite of **Residual sugar**, But with better spread in our plot, we can observe as the **Alcohol** increase the **Density** will decrease.

### Total Sulfur Dioxide x Free Sulfur Dioxide

```{r echo=FALSE, warning=FALSE}
ggplot(aes(x = total.sulfur.dioxide , y = free.sulfur.dioxide), data = winedata) +
  geom_jitter(alpha = 5/10) +
  coord_cartesian(xlim = c(0, 300), ylim = c(0, 100))+
  geom_smooth(method = 'lm')
```

Here we have a positive relationship, But with a much wider spread in our data.

### Total Sulfur Dioxide x Density

```{r echo=FALSE, warning=FALSE}
ggplot(aes(x = total.sulfur.dioxide, y = density), data = winedata) +
  geom_point(alpha = 5/10) +
  coord_cartesian(xlim = c(0, 300), ylim = c(0.985, 1.005)) +
  geom_smooth(method = 'gam', formula = y ~ s(x, bs = "cs"))
```

Here have an odd positive relationship here, we can see in our line that it start's with a smooth straight line, and then it goes up around 100 **Total Sulfur Dioxide** and stops around 200 with another smooth straight line.

### Alcohol x Residual Sugar

```{r echo=FALSE, warning=FALSE}
ggplot(aes(x = alcohol , y = residual.sugar), data = winedata) +
  geom_point(alpha = 5/10) +
  coord_cartesian(ylim = c(0, 30)) +
  geom_smooth(method = 'gam', formula = y ~ s(x, bs = "cs"))
```

**Alcohol** and **Sugar** have a negative relationship, We can see when **Alcohol** increases the **Residual Sugar** decrease but not by much.

# Bivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?

I Analyzed **Quality** with each Variable, **Alcohol** Had the strongest correlation with **Quality** And in the boxplot it showed us that **Alcohol** have an effect on the **Quality** of wine, Followed up by **Density** with the strongest negative correlation which showed us having a lower **Density** may lead to better **Quality**, What is interesting that the correlation between **Alcohol** and **Density** is the strongest negative correlation in the entire matrix.

### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?

**Density** has the strongest positive and negative correlation in the matrix, The strongest positive correlation is with **Residual Sugar** And the strongest negative correlation is with **Alcohol**, Also **Density** have a lot more strong correlations.

### What was the strongest relationship you found?
The strongest relationship is between **Density** and **Residual Sugar**.

# Multivariate Plots Section

### Residual Sugar x Density x Rating

```{r echo=FALSE, warning=FALSE}
ggplot(aes(x = residual.sugar, y = density, color = rating), data = winedata) +
  geom_point(alpha = 1, size = 1, position = 'jitter') +
  geom_smooth(method = 'lm', se = FALSE) +
  scale_color_brewer(type = 'qual', palette = 3) +
  coord_cartesian(ylim = c(0.985, 1.005)) +
  scale_x_log10()
```

In this plot I can see that most of the good **Quality** wines have **Density** around 0.990, and most of the good wines are between 3 and 10 **Residual Sugar**(log10 scaled).

### Alcohol x Density x Rating

```{r echo=FALSE, warning=FALSE}
ggplot(aes(x = alcohol, y = density, color = rating), data = winedata) +
  geom_point(alpha = 1, size = 1, position = 'jitter') +
  geom_smooth(method = 'lm', se = FALSE) +
  scale_color_brewer(type = 'qual', palette = 'Set2') +
  coord_cartesian(ylim = c(0.985, 1.005))
```

In this plot I can't really tell a lot, Average **Rating** dots covers most of the plot, And our line is almost the same level, I can see that there are a lot of good **Quality** dots at the end of the tail. 

### Total Sulfur Dioxide x Free Sulfur Dioxide x Rating

```{r echo=FALSE, warning=FALSE}
ggplot(aes(x = total.sulfur.dioxide, y = free.sulfur.dioxide, color = rating), data = winedata) +
  geom_point(alpha = 1, size = 1, position = 'jitter') +
  geom_smooth(method = 'gam', se = FALSE) +
  scale_color_brewer(type = 'qual', palette = 1) +
  coord_cartesian(xlim = c(0, 300), ylim = c(0, 100))
```

The Average **Rating** in this plot is almost all over the plot, I can see that most of the good **Quality** wine is around 25 to 60 **Free Sulfur Dioxide** and around 75 to 150 **Yotal Sulfur Dioxide**.

### Total Sulfur Dioxide x Density x Rating

```{r echo=FALSE, warning=FALSE}
ggplot(aes(x = total.sulfur.dioxide, y = density, color = rating), data = winedata) +
  geom_point(alpha = 1, size = 1, position = 'jitter') +
  geom_smooth(method = 'lm', se = FALSE) +
  scale_color_brewer(type = 'seq', palette = 2) +
  coord_cartesian(xlim = c(0, 300), ylim = c(0.985, 1.005)) 
```

Again, I can observe that having low **Density** might lead to having good **Quality** wines.

### Alcohol x Residual Sugar x Rating

```{r echo=FALSE, warning=FALSE}
ggplot(aes(x = residual.sugar, y = alcohol, color = rating), data = winedata) +
  geom_point(alpha = 1, size = 1, position = 'jitter') +
  geom_smooth(method = 'lm', se = FALSE) +
  scale_color_brewer(type = 'qual', palette = 6) +
  scale_x_log10()
```

In this plot I can see that most Good **Quality** wine has **Alcohol** more than 11 and it's showing clearly in this plot.



# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

I Explored the strongest correlations in the dataset with **Rating** of **Quality** of the wine, and i've observed that having high **Alcohol** and a good amount of **Residual Sugar** and low **Density** might lead to having a good **Quality** wine.

### Were there any interesting or surprising interactions between features?
I Did not see any surpising interactions.

------

# Final Plots and Summary

### Plot One
```{r echo=FALSE, Plot_One}
ggplot(data = winedata, aes( x = ordered(quality), y=alcohol, fill = ordered(quality))) + 
  geom_boxplot(show.legend = FALSE) +
  geom_jitter(alpha = 0.2/10, show.legend = FALSE) +
  scale_y_continuous(breaks = seq(5,15,1)) +
  stat_summary(fun.y = mean, geom = 'point', shape = 8,size = 2, show.legend = FALSE) +
  scale_fill_brewer(type = 'seq', palette = 'Greens') +
  labs(title = "Effect of Alcohol on The Wine Quality",
       x = "Quality", 
       y = "Alcohol (% by Volume)")
```

### Description One

**Alcohol** seems to have the most impact on the **Quality** of the wine as shown in the boxplot, in this plot we can see that as the **Alcohol** volume goes up the **Quality** of the wine increases as well, I Added a mean pointer and i can observe the same thing that wine **Alcohol** increases the mean/median for **Quality** increase.

### Plot Two
```{r echo=FALSE, Plot_Two}
ggplot(aes(x = residual.sugar, y = density, color = rating), data = winedata) +
  geom_point(alpha = 7/10, size = 1, position = 'jitter') +
  geom_smooth(method = 'lm', se = FALSE) +
  scale_color_brewer(type = 'seq', palette = 4) +
  theme_dark() +
  theme(legend.position = "bottom") +
  coord_trans(x = 'log10', 
              limx = quantile((winedata$residual.sugar), c(0.001, 0.999)),
              limy = c(0.987, 1.003)) +
  scale_x_continuous(breaks = seq(0, 20, 2)) +
  scale_y_continuous(breaks = seq(0.987,1.003,0.002)) +
  labs(title = "Residual Sugar x Density on Wine Quality",
       x = "Residual Sugar (g / dm^3)",
       y = "Density (g / cm^3)",
       color = "Quality of wine:")
```

### Description Two

**Density** and **Residual Sugar** has the strongest correlation in our data, And through my analysis it seems that **Residual Sugar** and **Density** also effect the **Quality** of wine, I can see most of good **Quality** wine have a line lower than average and bad wines.

### Plot Three
```{r echo=FALSE, Plot_Three}
ggplot(aes(x = residual.sugar, y = alcohol, color = rating), data = winedata) +
  geom_point(alpha = 7/10, size = 1, position = 'jitter') +
  geom_smooth(method = 'lm', se = FALSE) +
  scale_color_brewer(type = 'qual', palette = 6) +
  theme_bw() +
  theme(legend.position = "bottom") +
  coord_trans(x = 'log10', 
              limx = quantile((winedata$residual.sugar), c(0.001, 0.999)),
              limy = c(8, 14)) +
  scale_x_continuous(breaks = seq(0, 20, 2)) +
  scale_y_continuous(breaks = seq(8, 14, 1)) +
  labs(title = "Residual Sugar x Alcohol On Wine Quality",
       x = "Residual Sugar (g / dm^3)",
       y = "Alcohol (% by Volume)",
       color = "Quality of wine:")
```

### Description Three

**Alcohol** and **Residual sugar** have a negative correlation, in this plot we can see that we have a lot of good **Quality** wine in the upper area of the plot, and i came to the conclusion that **Alcohol**, **Density** and **Residual Sugar** effect the **Quality** of the wine.

------

# Reflection

In this project I started with exploring each variable in our dataset, since we only have 12 variables to explore it wasn't a struggle to look at them, most of the variables have a normal distribution and some are positively skewed, I didn't observe a lot in the first section, then I started to explore between 2 variables, but before I started, I created a correlation matrix to observe the strongest correlation with **Quality** and other strong correlations, after that i looked at multivariate plots, to explore 2 variables on the **Rating** of wine **Quality**.

My goal was to know which chemical properties affect the **Quality** of wine, the first thing i knew that effect the **Quality** of wine is **Alcohol**, it showed me a clear trend that when **Alcohol** increase the **Quality** and **Rating** of the wine increases as well, also **Residual Sugar** and **Density** showed me that they are a factor as well in affecting the **Quality** of the wine.

One of the things I struggled with is with multivariate plots, it seemed that I didn't really observe a lot of things and the plots doesn't seem to show much, one of the things that I can do in the future is using machine learning techniques to predict what could make the perfect wine **Quality**.